Hyperbolicity of Augmented Links in the Thickened Torus

### 2022-04-06 main.tex
address main concerns of reviewer, left with errata to fix

\begin{define}
Recall that a \emph{twist region}
in a link diagram is a maximal sequence of vertices
such that consecutive vertices are two vertices of a bigon face,
and consecutive bigons meet only at a vertex (not an edge).
We say that the \emph{direction} of a twist region
is the pair of faces (possibly the same face)
that are across from the bigons at the end;
if a twist region consists of only one vertex,
a direction is a pair of opposite faces (again, possibly the same face)
meeting at the crossing.
We say that a twist region consisting of only one vertex
is \emph{trivial}.
%%\footnote{There is an ambiguity of ``maximality'' in this definition:
%%for example, if a vertex of a link diagram meets exactly one bigon,
%%it can be considered as part of a twist region of length 2
%%(given by that bigon),
%%or it can be considered as part of a twist region of length 1,
%%as there are no bigons in the other ``direction''.
%%It should be clear which ``direction'' a twist region is going
%%when we deal with augmentations later.
%%}

@@

\begin{prop}\label{p:tori_decomp}
Let $K$ be an alternating link in the thickened torus
with a cellular link diagram,
and let $L$ be an augmented link obtained from $K$.
%Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
There is a decomposition of the complement,
$(\torus \times I) - L$, into two ideal torihedra;
the graphs of the torihedra are $\Gamma_T(L)$ and $\Gamma_B(L)$.
\end{prop}

@@

@@

More generally, if $K$ is as above with a twist-reduced diagram
containing bigons,
and $L$ is obtained by augmenting $K$
such that every twist region with at least one bigon is augmented,
%(and possibly other crossings),
then $L$ is hyperbolic.
\end{theorem}

@@

Recall that $\Gamma_T(L),\Gamma_B(L)$ are
obtained by bow-tie modifications of the diagram $D'$
of a link $K'$
(see \defref{d:tori-decomp-graph}).
Assign to each edge $e$ of $D'$ the angle $\theta_e = \pi/2$
(so that $\theta_e^* = \pi/2$ too).
Using the fact that $K'$ is weakly prime
(which easily follows from $K$ being weakly prime),
it is not hard to see that the condition on cocycles
of \thmref{t:bs-thm4} is satisfied by this assignment.
Thus, there exists a non-degenerate angle-splitting
$\vphi_\bullet$ of $(D',\theta_\bullet^*)$.
%Recall from the proof of \prpref{p:tori_decomp}
%that the two graphs $\Gamma_T(L),\Gamma_B(L)$
%can be obtained by modifying the link diagram of $K$:
%we take $K'$ to be the link that agrees with $K$ everywhere
%except each augmented twist region has only one crossing,
%and $\Gamma_T(L),\Gamma_B(L)$ are

@@

>>>>

\begin{define}
Recall that a \emph{twist region}
in a link diagram is a maximal sequence of vertices
such that consecutive vertices are two vertices of a bigon face,
and consecutive bigons meet only at a vertex (not an edge).

TODO terrible defn.

We say that the \emph{direction} of a twist region
is the pair of faces (possibly the same face)
that are across from the bigons at the end;
if a twist region consists of only one vertex,
a direction is a pair of opposite faces (again, possibly the same face)
meeting at the crossing.
We say that a twist region consisting of only one vertex
is \emph{trivial}.
%%\footnote{There is an ambiguity of ``maximality'' in this definition:
%%for example, if a vertex of a link diagram meets exactly one bigon,
%%it can be considered as part of a twist region of length 2
%%(given by that bigon),
%%or it can be considered as part of a twist region of length 1,
%%as there are no bigons in the other ``direction''.
%%It should be clear which ``direction'' a twist region is going
%%when we deal with augmentations later.
%%}

@@

\begin{prop}\label{p:tori_decomp}
Let $K$ be an alternating link in the thickened torus
with a cellular link diagram,
and let $L$ be an augmented link obtained from $K$.
%Let $G(L)$ be a diagram of the link on $\torus \times \{0\}$.
There is a decomposition of the complement,
$(\torus \times I) - L$, into two ideal torihedra.

Moreover, the graphs of the torihedra are
the top and bottom bow-tie graphs from
\defref{d:tori-decomp-graph},
$\Gamma_T(L)$ and $\Gamma_B(L)$,
respectively.

We call this the
\emph{torihedral decomposition of
the link complement of $L$ in the thickened torus}.
\end{prop}

@@

TODO rephrase to more careful.

@@

More generally, if $K$ is as above with a twist-reduced diagram
containing bigons,
and $L$ is obtained by augmenting $K$
such that for every twist region with at least one bigon,
either the twist region is augmented,
or each vertex of the twist region is augmented
in the other direction,
or both.
%(and possibly other crossings),
then $L$ is hyperbolic.
\end{theorem}

% awkward attempts to address necessity of bigon condition
% in main theorem
%\begin{remark}
%In the torihedral decomposition of $L$
%(as in \prpref{p:tori_decomp}),
%a string of bigons would
%produce bow-tie graphs whose total number 
%of edges identified is greater than 4 
%
%
%We put restrictions on bigons for the following reason.
%Recall from \prpref{p:tori_decomp} that
%a link complement is obtained from identifying
%certain collections of edges from the top and bottom torihedra.
%When there are non-augmented bigons,
%some of these collections would not be 
%\end{remark}

@@

Recall that $\Gamma_T(L),\Gamma_B(L)$ are
obtained by bow-tie modifications of the diagram $D'$
of a link $K'$
(see \defref{d:tori-decomp-graph}).
Assign to each edge $e$ of $D'$ the angle $\theta_e = \pi/2$
(so that $\theta_e^* = \pi/2$ too).
This assignment has the property that
the sum of dihedral angles around each identified edge
(in the complement of $K'$) is $2\pi$.
This can be achieved because of the hypotheses on bigons
in our theorem statement.

Using the fact that $K'$ is weakly prime
(which easily follows from $K$ being weakly prime),
it is not hard to see that the condition on cocycles
of \thmref{t:bs-thm4} is satisfied by this assignment.
Thus, there exists a non-degenerate angle-splitting
$\vphi_\bullet$ of $(D',\theta_\bullet^*)$.
%Recall from the proof of \prpref{p:tori_decomp}
%that the two graphs $\Gamma_T(L),\Gamma_B(L)$
%can be obtained by modifying the link diagram of $K$:
%we take $K'$ to be the link that agrees with $K$ everywhere
%except each augmented twist region has only one crossing,
%and $\Gamma_T(L),\Gamma_B(L)$ are

@@

\begin{remark}
Note that for our definition of augmentation,
we exclude the case where
an unknotted circle component is added around
two parallel strands that do not meet at a crossing.
In particular, this implies that
a non-weakly prime link cannot become weakly prime
under augmentation.

If we have an augmentation around two such parallel strands,
we may consider the related link
where those two strands have a full twist;
the hyperbolicity is unaltered, and
\thmref{t:auglink_hyp} would apply.
\end{remark}
